---
title: "Week 10 Assignments"
author: "Zoucha, Michael"
date: "11/2/2021"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
library(tidyverse)
library(report)
library(caTools)
```

# Assignment 1

```{r echo = FALSE, include = FALSE}
thoracic_df <- read.csv("thoracic_surgery_data.csv")

## Substring size, diagnosis, performance to make all numbers
summary(thoracic_df)

survival_regression <- glm(Risk1Yr ~ Diagnosis + FVC + FEV1 + Performance + PainBefore + HaemoptysisBefore + DsponeaBefore + CoughBefore + WeaknessBefore +
                             Size + Diabetes + MI + PAD + Smoking + Asthma + AGE, data = thoracic_df, family = 'binomial')
summary(survival_regression)
```

- The effect of DsponeaBefore is statistically significant and positive (beta = 1.37, 95% CI [0.38, 2.31], p = 0.005; Std. beta = 1.37, 95% CI [0.38, 2.31])
- The effect of Size is statistically significant and positive (beta = 1.65, 95% CI [0.43, 2.85], p = 0.007; Std. beta = 1.65, 95% CI [0.43, 2.85])
- The effect of Diabetes is statistically significant and positive (beta = 0.93, 95% CI [0.02, 1.78], p = 0.037; Std. beta = 0.93, 95% CI [0.02, 1.78])
- The effect of Smoking is statistically significant and positive (beta = 1.08, 95% CI [0.18, 2.16], p = 0.030; Std. beta = 1.08, 95% CI [0.18, 2.16])

```{r echo = FALSE, include = TRUE}
split <- sample.split(thoracic_df, SplitRatio = 0.8)
train_data <- subset(thoracic_df, split == "TRUE")
test_data <- subset(thoracic_df, split == "FALSE")

thoracic_df$Diagnosis <- as.factor(substring(thoracic_df$Diagnosis, 4, 4))
thoracic_df$Performance <- as.factor(substring(thoracic_df$Performance, 4, 4))

survival_regression_train <- glm(Risk1Yr ~ Diagnosis + DsponeaBefore + Size + Diabetes + Smoking + AGE + Performance, data = train_data, family = binomial(link = "logit"))
summary(survival_regression_train)

res <- predict(survival_regression_train, test_data, type="response")

res <- predict(survival_regression_train, train_data, type="response")

confmatrix <- table(Actual_Value = train_data$Risk1Yr, Predicted_Value = res > 0.5)
confmatrix
(confmatrix[[1,1]] + confmatrix[[2,2]]) / sum(confmatrix)
```
\newpage
# Assignment 2
```{r echo = FALSE, include = TRUE}
binary_df <- read.csv("/Users/Shared/OneDrive - Bellevue University/DSC 520 - Statistics for Data Science/mkzoucha_dsc520/dsc520/data/binary-classifier-data.csv")

summary(binary_df)

split <- sample.split(binary_df, SplitRatio = 0.8)
train_data <- subset(binary_df, split == "TRUE")
test_data <- subset(binary_df, split == "FALSE")

binary_regression <- glm(label ~ x + y, data = train_data, family = 'binomial')
summary(binary_regression)

res <- predict(binary_regression, test_data, type="response")
res <- predict(binary_regression, train_data, type="response")

confmatrix <- table(Actual_Value = train_data$label, Predicted_Value = res > 0.5)
confmatrix

(confmatrix[[1,1]] + confmatrix[[2,2]]) / sum(confmatrix)
```